\documentclass{article}

\usepackage{amsmath}

\newcommand{\rr}{\mathbf{r}}
\newcommand{\ii}{\mathbf{i}}
\newcommand{\jj}{\mathbf{j}}
\newcommand{\kk}{\mathbf{k}}

\begin{document}

{\bf Quiz \#8; Tuesday, date: 03/13/2018}

{\bf MATH 53 Multivariable Calculus with Stankova}

{\bf Section \#117; time: 5 -- 6:30 pm}

{\bf GSI name: Kenneth Hung}

{\bf Student name:}

\vspace*{0.25in}

\begin{enumerate}
\item Find the directions in which the directional derivative of $f(x, y) = y^3 + y x^2$ at the point $(0, 1)$ has the value $1$.

{\em Solution.} The gradient of $f$ is $\langle 2xy, 3y^2 + x^2\rangle$. At $(0, 1)$ this is $\langle 0, 3\rangle$. If a unit vector $\mathbf{u}$ gives a directional derivative of $1$, then we must have
\[
\langle 0, 3 \rangle \cdot \mathbf{u} = 1.
\]
Suppose $\mathbf{u} = \langle \cos \theta, \sin \theta\rangle$, then
\[
3 \sin \theta = 1 ~~~~ \Longrightarrow ~~~~ \sin \theta = \frac{1}{3},
\]
which means $\cos \theta = \pm \frac{\sqrt{8}}{3}$. So the unit vector $\mathbf{u}$ is $\langle \pm \frac{\sqrt{8}}{3}, 1 \rangle$.

\item {\em True / False?} The normal vector to the surface $z = f(x, y)$ is three-dimensional, while the normal vector to the level curve of $z = f(x, y)$ is two-dimensional.

{\em Solution.} {\bf True.} The surface $z = f(x, y)$ is a three-dimensional object, so the normal vector lives in the same space. The level curve lives in a two-dimensional space, so the normal vector to that lives in the two-dimensional space as well.

\item {\em True / False?} The surface $z = x^2 - xy - y^2$ has a saddle point.

{\em Solution.} {\bf True.} We start by finding all critical points. We take first derivatives:
\[
\frac{\partial z}{\partial x} = 2x - y, ~~~~ \frac{\partial z}{\partial y} = -x -2y.
\]
Setting both of these to zero gives a unique solution of $(x, y) = (0, 0)$. It remains to check what $D$ is. We have
\[
\frac{\partial^2 z}{\partial x \partial x} = 2, ~~~~ \frac{\partial^2 z}{\partial x \partial y} = \frac{\partial^2 z}{\partial y \partial x} = -1, ~~~~ \frac{\partial^2 z}{\partial y \partial y} = -2
\]
so
\[
D = \begin{vmatrix}
2 & -1 \\
-1 & -2
\end{vmatrix} = -5,
\]
which is negative. So $(0, 0)$ is a saddle point.
\end{enumerate}

\end{document}