\documentclass{article}

\usepackage{amsmath}

\newcommand{\rr}{\mathbf{r}}

\begin{document}

{\bf Quiz \#5; Tuesday, date: 02/20/2018}

{\bf MATH 53 Multivariable Calculus with Stankova}

{\bf Section \#114; time: 2 -- 3:30 pm}

{\bf GSI name: Kenneth Hung}

{\bf Student name: SOLUTIONS}

\vspace*{0.25in}

\begin{enumerate}
\item At what point does the curve have maximum curvature? What happens to the curvature as $x \to \pi / 2$?
\[
y = \ln (\sec x), ~~~~ 0 \le x < \frac{\pi}{2}.
\]

{\em Solution.} To apply the formula for curvature, we need the first two derivatives, which are
\begin{align*}
y' = \frac{\sec x \tan x}{\sec x} = \tan x, \\
y'' = \sec^2 x.
\end{align*}
Now by Formula 11 on pg.\ 865, we have
\[
\kappa(x) = \frac{|\sec^2 x|}{\left(1 + \tan^2 x\right)^{3/2}} = \frac{\sec^2 x}{\sec^3 x} = \cos x.
\]

The curve has maximum curvature at $x = 0$, and the curvature approaches $0$ as $x \to \pi / 2$.

\item {\em True / False?} If a curve is parametrized by its arc length, there is no tangential component of acceleration and the normal component of acceleration is the curvature.

{\em Solution.} {\bf True.} Since the curve is parametrized by its arc length, we have $v(t) = 1$. By Formula 7 on pg.\ 874, the tangential component is $v'$, which is zero, and the normal component is $\kappa v^2 = \kappa$, which is just the curvature.

\item {\em True / False?} The level surfaces of $f(x, y, z) = x^2 + y^2 - z$ are elliptic paraboloids, that can be obtained from each other by shifting in the $z$-direction.

{\em Solution.} {\bf True.} The level surfaces are $x^2 + y^2 - z = k$ for some $k$, or equivalently,
\[
z + k = x^2 + y^2,
\]
which can be obtained by shifting the elliptic paraboloid $z = x^2 + y^2$ by $k$ units in the negative $z$-direction.
\end{enumerate}

\end{document}