\documentclass{article}

\usepackage{amsmath,amsfonts,tikz}

\newcommand{\ii}{\mathbf{i}}
\newcommand{\jj}{\mathbf{j}}
\newcommand{\kk}{\mathbf{k}}
\newcommand{\rr}{\mathbf{r}}
\newcommand{\vv}{\mathbf{v}}
\newcommand{\aaa}{\mathbf{a}}
\newcommand{\TT}{\mathbf{T}}
\newcommand{\NN}{\mathbf{N}}
\newcommand{\BB}{\mathbf{B}}

\begin{document}

{\bf Worksheet \#23; date: 04/12/2018}

{\bf MATH 53 Multivariable Calculus}

\begin{enumerate}
\item {\em True / False?} $\mathbf{F}(x, y) = \langle x^2, y^2 \rangle$ is a conservative vector field.

\item {\em True / False?} Suppose $f$ is a scalar function and $\nabla f$ is a force field. The work done by this force field along any one level curve of $f$ is zero.

\item {\em True / False?} If we overlay a sketch of the gradient vector field $\nabla f$ and the contour map $f$, the arrows from the vector field will always be perpendicular to the contour lines.

\item {\em True / False?} Suppose $f$ is a nonnegative function and $C$ is the curve parametrized as
\[
x = a + (b - a)t, ~~~~ y = 0, ~~~~ 0 \le t \le 1
\]
Then $\int_C f(x, y) \,ds \ge 0$ but $\int_a^b f(x, y) \,dx$ maybe negative.

\item {\em (Stewart 16.3.7)} Determine whether or not $\mathbf{F}$ is a conservative vector field. If it is, find a function $f$ such that $\mathbf{F} = \nabla f$.
\[
\mathbf{F}(x, y) = (ye^x + \sin y) \ii + (e^x + x \cos y) \jj
\]

\item {\em (Stewart 16.3.9)} Determine whether or not $\mathbf{F}$ is a conservative vector field. If it is, find a function $f$ such that $\mathbf{F} = \nabla f$.
\[
(y^2 \cos x + \cos y) \ii + (2y \sin x - x \sin y) \jj
\]

\item {\em (Stewart 16.3.17)} Find a function $f$ such that $\mathbf{F} = \nabla f$ and use this to evaluate $\int_C \mathbf{F} \cdot d\rr$ along the given curve $\mathbf{C}$.
\[
\mathbf{F}(x, y, z) = yze^{xz} \ii + e^{xz} \jj + xye^{xz} \kk,
\]
where $C$ is $\rr(t) = (t^2 + 1) \ii + (t^2 - 1) \jj + (t^2 - 2t) \kk$, $0 \le t \le 2$.

\item {\em (Stewart 16.3.23)} Find the work done by the force field $\mathbf{F}$ in moving an object from $P$ to $Q$.
\[
\mathbf{F}(x, y) = x^3 \ii + y^3 \jj, ~~~~ P(1, 0), Q(2, 2)
\]

\item {\em (Stewart 16.3.31)} Determine whether or not the given set is open, is connected, and is simply-connected.
\[
\{(x, y) \;|\; 0 < y < 3\}
\]

\item {\em (Stewart 16.3.33)} Determine whether or not the given set is open, is connected, and is simply-connected.
\[
\{(x, y) \;|\; 1 \le x^2 + y^2 \le 4, y \ge 0\}
\]
\end{enumerate}

\end{document}